\section{Limitations and further work}

As said, in this very first version a user must sign in with Google Games.
This is necessary because we identify users with GGames usernames.

Anyway, since this an Android application, users must have a Gmail address and
must have registered that in Android.

Furthermore, if a user is interested in Games they will probably have a Games
account.
This is why we don't think this is a big limitation.
A number of solutions are possible to address that.
For example we could provide a full enrollment mechanism, asking users to sign
up with email and password. We chose not to do that because it would required
an effort out of the scope of this application.  \\

Another feasible line for further work is represented by offline duels.
Currently QuizFight supports only online multi-round duels, but it could be
used for mono or multi-round duels without the need of Internet connectivity.
In this case, a cheaper connection technology, such as Bluetooth or
WiFi-Direct, is suitable for connecting two or even more devices.
This would partially solve the aforementioned mandatory-sign-in limitation,
since such duels are feasible even without a sign up (but of course they would
not be considered in achievements and Google-related statistics). \\

Currently, QuizFight supports only true/false or multiple-choice questions.
A clever application could offer support for different question types, such as
open questions.
That would require a natural language parser, probably supported by some kind of AI
algorithms.
We could also provide funnier way to dare players, such as group duels. \\

Lastly, it has to be noted that currently only authorized users are able to sign
in, both with Facebook and Google. In fact, since QuizFight has not been
published, only the developers may log in. This is not a limitation in the 
common sense, since once published the problem disappears. Anyhow, until then,
we have to explicitly authorize every user via both Google and Facebook Identity
and Access Management's engines. Further, since the authorization process 
requires an SSH key to be used, even the actual Android Studio's instance must
be allowed to execute the application. 
